% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
%
\title{PhD Cycle 39 First Year Final Report
%\thanks{Supported by organization x.}
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Nicolas Farabegoli\inst{1}\orcidID{0000-0002-7321-358X}}
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
    Alma Mater Studiorum -- Università di Bologna, Cesena FC 47522, Italy
    \email{nicolas.farabegoli@unibo.it}
}
%
\maketitle              % typeset the header of the contribution
%
% \begin{abstract}
% The abstract should briefly summarize the contents of the paper in
% 150--250 words.

% \keywords{First keyword  \and Second keyword \and Another keyword.}
% \end{abstract}
%
%
%
\section{Research Activities and Outcomes}

During the first year of my PhD,
I have been working on the development of innovative models fostering the deployment independence of collective adaptive systems (CAS).

In particular,
based on previous work on the pulverisation~\cite{DBLP:journals/iotj/CasadeiFPPSV22,DBLP:journals/fi/CasadeiPPVW20} --
a modern approach to partition into independent components the execution model of CAS --
I proposed a practical framework implementing the pulverisation model,
and extending it to support the dynamic reconfiguration at runtime.
%
The proposed framework and the extended model with reconfiguration rules have been validated through a set of experiments,
showing the feasibility of the approach and the benefits in terms of deployment independence and non-functional properties,
like cost, power consumption, and performance.
%
The results of the experiments have been published in a paper submitted to the journal \emph{Future Generation Computer Systems journal}~\cite{DBLP:journals/fgcs/FarabegoliPCV24}.

Subsequently,
I have been working on the development of a novel approach to better support the dynamic reconfiguration of CAS based on the pulverisation model:
pre-defined reconfiguration rules may not be sufficient to cover all possible scenarios,
and they may lead to suboptimal solutions,
like oscillator behaviors.
%
To address this issue,
I proposed to shift the perspective from local reconfiguration rules to a global perspective,
where the system's reconfiguration is expressed by a collective program,
leveraging \emph{Aggregate Computing}.
%
In this contribution,
I proposed a general pulverisation framework architecture where dynamic components' reconfiguration is captured as a first-class citizen,
and I proposed a novel (collective) algorithm to balance the system's load during the reconfiguration process.
%
The proposed approach has been validated through a set of experiments,
showing that the proposed algorithm can better adapt to disruptive and changing conditions,
and it can provide better performance and stability compared to allocations defined a priori.
%
The results of the experiments and the proposed approach have been submitted and currently under review to the journal \emph{Internet of Things; Engineering Cyber Physical Human Systems}~\cite{farabegoli4798700dynamic}.

Finally,
I worked on the development of a novel approach to partition the program specification of CAS into independent functions (or services) to achieve flexible deployment in the \emph{Edge-cloud Continuum}.
%
This contribution is orthogonal to the pulverisation model,
and it aims to provide a more flexible and fine-grained approach to partition the system's program specification.
%
The proposed model has been formalised via an operational semantics,
and properties like self-stabilisation preservation, and deployment independence have been formally proved.
%
The new model has been validated through a set of experiments,
showing empirically that the proposed approach preserves the same functional behavior of the original (monolithic deployed) system,
and it can provide non-functional benefits in terms of power consumption and performance by paying a small overhead in terms of communication.
%
The results of the experiments and the proposed approach have been accepted and presented at the \emph{ACSOS 2024} conference~\cite{DBLP:conf/acsos/FarabegoliFAVE24}.

% \subsection{Research Goals}

% \subsection{Literature Review}

\section{Self Evaluation}

\section{Academic Activities}

\subsection{Tutoring Activities}

In this first year of my PhD,
I have been involved in tutoring activities for the course \textbf{PROGRAMMAZIONE AD OGGETTI [cod. 70219]} for the Bachelor's Degree in Computer Science and Engineering for the academic year 2023/2024,
and currently involved in the academic year 2024/2025 edition of the same course.

\subsection{Doctoral School and Courses}

I've attended the \textbf{Bertinoro International Spring School 2024} in March 2024,
in particular I've attended the \emph{Graph Neural Network} course by Prof. Fabrizio Silvestri,
the \emph{Program analysis: from proving correctness to proving incorrectness} course by Prof. Roberto Bruni and Robera Gori,
and the \emph{Large Language Models} course by Prof. Danilo Croce.

Moreover,
I've attended the following PhD courses:
\begin{itemize}
    \item \emph{How to Write and Publish a Research Paper in Computer Science and Engineering} by Prof. Zeynep Kiziltan;
    \item \emph{Risk Assessment of Machine Learning for Cybersecurity} by Prof. Fabio Pierazzi;
    \item \emph{Introduction to complex systems science} by Prof. Andrea Roli;
\end{itemize}

At the end of the first year,
I've obtained \textbf{15} CFU with evaluation, and \textbf{4} CFU without evaluation.

\section{Next Year Plan}


%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\nocite{*}
\bibliographystyle{splncs04}
\bibliography{bibliography}

\end{document}
